Data Processing

### 2019-11-15 analysis/data_processing.Rmd
fix bug

data <- raw_data %>%
  filter(trial != "training", 
         trial != "filler1", 
         trial != "filler2",
         trial != "train",
         trial != "train2")%>%
  filter(phase == "shape" | is.na(phase))%>%
  select(subid, subage, test_date, task, trial, correct)%>%
  mutate(subid = str_replace(subid,"-","_"))%>%
  separate(subid, into = c("id","test_day"), sep="_")

>>>>

data <- raw_data %>%
  filter(trial != "training", 
         trial != "filler1", 
         trial != "filler2",
         trial != "train",
         trial != "train2")%>%
  filter(phase == "shape" | is.na(phase))%>%
  select(subid, subage, test_date, task, trial, correct)%>%
  separate(subid, into = c("id","test_day"), sep="\\.")
